### 2020-06-21 docs/LaTex/Paper.tex
Fixes bad pin definition in .ino sketch and completes docs

@@

Basically the sketch is based on the \href{https://github.com/mcci-catena/arduino-lmic/blob/master/examples/ttn-abp/ttn-abp.ino}{ttn-abp example}, as the reader can see in the first comment block; that example sends a LoRaWAN valid package with the payload \enquote{Hello World!}.

>>>>

\definecolor{dkgreen}{rgb}{0,0.6,0}
\definecolor{dred}{rgb}{0.545,0,0}
\definecolor{dblue}{rgb}{0,0,0.545}
% \definecolor{lgrey}{rgb}{0.9,0.9,0.9}
% \definecolor{gray}{rgb}{0.4,0.4,0.4}
\definecolor{darkblue}{rgb}{0.0,0.0,0.6}
\lstdefinelanguage{cpp}{
      backgroundcolor=\color{background},  
      basicstyle=\color{black}\mdseries\scriptsize\ttfamily,   
      % breakatwhitespace=false,       
      breaklines=true,               
      % captionpos=b,                   
      commentstyle=\color{dkgreen},   
      deletekeywords={...},          
      escapeinside={\%*}{*)},                  
      frame=lines,                  
      language=C++,                
      keywordstyle=\color{purple},  
      morekeywords={BRIEFDescriptorConfig,string,TiXmlNode,DetectorDescriptorConfigContainer,istringstream,cerr,exit}, 
      identifierstyle=\color{black},
      stringstyle=\color{blue},      
      numbers=left,                 
      numbersep=8pt,                  
      numberstyle=\scriptsize, 
      rulecolor=\color{black},        
      showspaces=false,               
      showstringspaces=false,        
      showtabs=false,                
      stepnumber=1,                   
      tabsize=5,                     
      title=\lstname,                 
    }

@@

Basically the sketch is based on the \href{https://github.com/mcci-catena/arduino-lmic/blob/master/examples/ttn-abp/ttn-abp.ino}{ttn-abp example}, as the reader can see in the first comment block; that example sends a LoRaWAN valid package with the payload \enquote{Hello World!}. Besides it uses the ABP (Activation-by-personalization) method ---in opposition to OTAA (Over-the-air-activation) method---, depending on the used method it is necessary to include different security keys provided by The Things Network stack in the code. \cite{TTN_Security}

As commented \href{https://github.com/mcci-catena/arduino-lmic/blob/master/examples/ttn-abp/ttn-abp.ino#L29}{lines 29 and 30} point, the most important thing before start working on the sketch is to configure the \cmd{arduino-lmic} library, so after install the library with the library manager ---in the Arduino IDE or any other chosen IDE---, the reader will need to go the library path and locate the \href{https://github.com/mcci-catena/arduino-lmic/blob/master/project_config/lmic_project_config.h}{\cmd{<lib\_path>/project\_config/lmic\_project\_config.h}} file to ensure the line 2 (\cmd{\#define CFG\_eu868 1}) is \textbf{uncommented} and the line 3 (\cmd{\#define CFG\_us915 1}) is \textbf{commented}. This is to enable specific functions in the library to the Europe region (where the radio regulations are slightly different than in other regions); so this \cmd{lmic\_project\_config.h} must looks like in te example \ref{ej:lmic_project_config.h}

\begin{lstlisting}[%
  % float=ht,
  language=cpp,
  firstnumber=1,
  caption={Configuring lmic library radio.},
  label=ej:lmic_project_config.h
  ]
  // project-specific definitions
  #define CFG_eu868 1
  //#define CFG_us915 1
  //#define CFG_au915 1
  //#define CFG_as923 1
  // #define LMIC_COUNTRY_CODE LMIC_COUNTRY_CODE_JP	/* for as923-JP */
  //#define CFG_kr920 1
  //#define CFG_in866 1
  #define CFG_sx1276_radio 1
  //#define LMIC_USE_INTERRUPTS
\end{lstlisting}

After this, the sketch may use specific functions to perform radio transmissions in Europe region. This in fact, will has an impact in the \cmd{void setup()\{\}} function ---in the example sketch ttn-abp--- so lines between \href{https://github.com/mcci-catena/arduino-lmic/blob/master/examples/ttn-abp/ttn-abp.ino#L232}{line 232} and line 254 will be executed when the library is configured for Europe region.

Once the library has been properly configured, the second most important thing is set the pin mapping for the chip
